---
title: "Mlr3 Asthma"
author: "bingmp"
date: "`r Sys.Date()`"
output:
    md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GSE152004
The folder named GSE152004 is the main bit of the data analysis process for the dataset GSE152004, including WGCNA analysis, differential gene analysis, volcano and heat maps, and more.

```{r}
list.files('1_GSE152004/')
list.files('1_GSE152004/code/')
```

## GSE67472
The folder named GSE67472 is the main bit of the data analysis process for the dataset GSE67472, including differential gene analysis, volcano and heat maps, and more.
```{r}
list.files('2_GSE67472/')
list.files('2_GSE67472/code/')
```

## mlr3
The folder named mlr3 is the main bit of the dataset federated data analysis process, including machine learning such as random forests and logistics regression, as well as shap analysis and more.

```{r}
list.files('3_mlr3/')
list.files('3_mlr3/code/')
```

